Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Finished disentangling

The function @continue@ is largely what we have for the second case in
@drive_step@, except a function call to @ndcontinue@ is placed when
the the normal continuation is empty.
Since we are analyzing a language in ANF, the first-order data representation of
continuation is simplified to @List@.
An empty list @Nil@ represents the halt of a computation path.
A cons @::@ means the top frame of the list holds the binding variable, and
evaluation context.
An analogue to this in standard CEK machines would be an abstract class (e.g., @cont@) with three
variants @halt@, @arg(value, cont)@ and @arg(exp, env, cont)@.

>>>>

@continue@ is largely what we have for the second case in
@drive_step@, except that @ndcontinue@ is called when
the normal continuation is empty.
Since we are analyzing a language in ANF, the first-order data representation of
continuations is simplified to a Scala @List@.
An empty list @Nil@ represents the halt of a computation path, whereas
a cons @::@ means the top frame of the list holds the binding variable and
evaluation context.
An analogy to this in standard CEK machines would be an abstract class (e.g., @cont@) with
three variants: @halt@, @arg(value, cont)@, and @arg(exp, env, cont)@.
